---
title: "Delaware River PIT tag data analysis"
author: "Ben Letcher"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, ecoh = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")

library(tidyverse)
library(lubridate)
library(knitr)
library(targets)
library(tarchetypes)

```

This notebook uses [targets](https://books.ropensci.org/targets/) to manage running code. Targets sets up dependencies among specified objects and only re-runs code as necessary. This can save run times for projects with models that take a while to run, like capture-mark-recapture models.  

Data preparation and model running happens using targets and exploration of the data and model runs is below in this Markdown document.  

'knit' the document to update all targets and exploration.  

'tar_make()' runs all the R scripts and functions specified in '_targets.R'. Only updated code or sections that are downstream from updated data are re-run.  
'tar_read()' reads 'target' data into the global environment.
```{r}
tar_make()

d <- tar_read(target_d)
eh <- tar_read(target_eh)
#str(d)
```


```{r}
tar_visnetwork()
```

Which rivers (Water) riverN corresponds to
```{r riverN}
table(d$Water, d$riverN)
```

### Raw data summary tables
```{r basic summaries}

kable(data.frame(ftable(d$date)))
kable(data.frame(ftable(d$Water, d$riverN)))
kable(data.frame(ftable(d$date)))
kable(data.frame(ftable(d$Water, d$riverN, d$date)))
kable(data.frame(ftable(d$species)))

length(unique(d$tag))
```

Group observations by month.  
Luckily, sampling periods do not span months, so we can use month as a grouping variable for sampling occasion
```{r by month}
kable(data.frame(ftable(d$dateYM)))
kable(data.frame(ftable(d$Water, d$riverN, d$dateYM)))
```

### Tag information
```{r tag information}

tagN <- d %>% 
  group_by(tag, Water) %>%
  summarize(n = n()) %>%
  filter(tag != "") %>%
  arrange(desc(n))

table(tagN$n)
(table(tagN$Water, tagN$n))

```

### Basic summary plots of raw data
```{r basic graphs}

ggplot(d %>% filter(!is.na(species)), aes(Length)) +
  geom_freqpoly() +
  facet_grid(species ~ Water)

```

```{r data for TAME}

# dTame <- d %>% 
#             select(Latitude, Longitude, tag, dateTime, species, Length, Weight) %>%
#             filter(tag != "", tag != "ad")
#             
# write.csv(dTame, './dataOut/dTame.csv', row.names = FALSE)

```



### Encounter histories
```{r eh}

str(eh$riverN)
head(eh$riverN)
```

